P4IRS: An Intermediate Representation and Compiler for Parallel and Performance-Portable Particle Simulations

### 2025-04-29 sage_latex_template/manuscript.tex
Add figure with P4IRS architecture
Signed-off-by: Rafael Ravedutti <rafael.r.ravedutti@fau.de>
Add caption for the new figure
Signed-off-by: Rafael Ravedutti <rafael.r.ravedutti@fau.de>

>>>>

\begin{figure*}[htb]
  \centering
  \includegraphics[width=0.75\textwidth]{pairs_architecture.pdf}
  \caption{\RMchange{P4IRS architecture. The user specifies the particle interactions to be computed, which are compiled to Python AST and further mapped to the P4IRS IR. Optimization choices and simulation setup must also be specified to determine which internal kernels are used, and the P4IRS IR is constructed in-place for the optimization routines based on the inputs. Many compilation passes are performed to transform the P4IRS IR before triggering the code generator. Finally, the optimized kernels, the data structures and the PairsSimulation interface class is generated, which can be used by the backend simulation code when not using whole-program generation (otherwise the full code is generated). The final binary can then be generated with any backend compiler the user chooses (GCC, CLANG, ICC, or other), and it must be linked with the Runtime Library, which is adapted to the generated simulation by using the P4IRS Metadata structure.}}
  \label{fig:features}
\end{figure*}
